Raw Traces

### 2023-05-23 Fish Data Analysis/Raw Traces Figure.qmd
Finished Figure 1

fish_len <- 0.083197
```

@@

```{r}
comp_data <- read.csv("Data/Fish_Raw_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
```

@@

### Final Version Dark
No flow

@@

@@

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

@@

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
  scale_color_manual(values = c("#ea4747","#df4415","#ff7489","#4790ea","#47ea4b", "#15c9df", "#8574ff", "#09b326"))+
  theme_classic()+ 
  theme(legend.position = "none")+
  xlab("Time (s)")+
  ylab("NND (BL)")+
  ylim(0,3)

@@

axis_remove <- list(showaxeslabels  = FALSE,
                    showgrid = FALSE,
                    showline = FALSE,
                    showticklabels = FALSE,
                    showspikes = FALSE,
                    showticklabels  = FALSE,
                    visible = FALSE,
                    zeroline = FALSE)

@@

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(0, 240, nnd_frame)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

@@

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
  scale_color_manual(values = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC"))+
  theme_classic()+ 
  theme(legend.position = "none")+
  xlab("Time (s)")+
  ylab("NND (BL)")+
  ylim(0,3)

@@

axis_remove <- list(showaxeslabels  = FALSE,
                    showgrid = FALSE,
                    showline = FALSE,
                    showticklabels = FALSE,
                    showspikes = FALSE,
                    showticklabels  = FALSE,
                    visible = FALSE,
                    zeroline = FALSE)

@@

>>>>

fish_len <- 0.083197
text_size = 20

@@

```{r}
comp_data <- read.csv("Data/3D_Trace_Fish_Comp_Values_3D.csv") %>% separate(Fish, c("Fish1", "Fish2"),sep="x") %>% mutate(Data_ID = paste(Year,Month,Day,Trial, sep = "_"))
```

@@

### Final Version Dark

No flow

@@

smooth_data_nnd_test_dark <- smooth_data_nnd %>% filter(Frame_Num %in% c(nnd_frame))

@@

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(240, nnd_frame)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

@@

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
  scale_color_manual(values = c("#ea4747","#df4415","#ff7489","#4790ea","#47ea4b", "#15c9df", "#8574ff", "#09b326"))+
  theme_classic()+ 
  theme(legend.position = "none")+
  xlab("Time (s)")+
  ylab("NND (BL)")+
  ylim(0,3)+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

ggsave("Paper Figures/Dark_NND_Raw.png", raw_nnd_plot, width = 6, height = 4)

axis_remove <- list(title = list(text = ""),
                    showaxeslabels  = FALSE,
                    showgrid = TRUE,
                    showline = FALSE,
                    showticklabels = FALSE,
                    showspikes = FALSE,
                    showticklabels  = FALSE,
                    visible = TRUE,
                    zeroline = FALSE)

@@

smooth_data_nnd_test_light <- smooth_data_nnd %>% filter(Frame_Num %in% c(nnd_frame))

select_frames_labeled <- example_data %>% select(c(Fish1,Frame_Num,Fish1_X,Fish1_Y)) %>%
                                          filter(Frame_Num %in% c(240, nnd_frame)) %>% 
                                          left_join(., smooth_data %>% select(Fish1, Frame_Num, Fish1_X_Smooth, Fish1_Y_Smooth, Fish1_Z_Smooth)) %>%
                                          group_by(Fish1, Frame_Num) %>%
                                          summarise(Fish1_X_Smooth = mean(Fish1_X_Smooth),
                                                    Fish1_Y_Smooth = mean(Fish1_Y_Smooth),
                                                    Fish1_Z_Smooth = mean(Fish1_Z_Smooth))

@@

raw_nnd_plot <- ggplot(smooth_data_nnd, aes(x = Frame_Num/60, y = Fish1_Distance_Smooth, color = Fish1))+
  geom_line(size = 1, alpha = 0.5)+
  geom_line(data = nnd_summary, aes(x = Frame_Num/60, y = meanNND_Smooth), color = "black", size = 1.5)+
  scale_color_manual(values = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC"))+
  theme_classic()+ 
  theme(legend.position = "none")+
  xlab("Time (s)")+
  ylab("NND (BL)")+
  ylim(0,3)+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.x = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

ggsave("Paper Figures/Light_NND_Raw.png", raw_nnd_plot, width = 6, height = 4)

axis_remove <- list(title = list(text = ""),
                    showaxeslabels  = FALSE,
                    showgrid = TRUE,
                    showline = FALSE,
                    showticklabels = FALSE,
                    showspikes = FALSE,
                    showticklabels  = FALSE,
                    visible = TRUE,
                    zeroline = FALSE)

@@

### Quick T Test

t.test(smooth_data_nnd_test_dark$Distance, smooth_data_nnd_test_light$Distance)
